Modeling Intervention Strategies for United States TB Control

### 2013-10-07 in_progress/presentations/paper/draft.tex
added abstract to paper

>>>>

\section{Abstract}
An extended epidemiological model for Tuberculosis in the US was developed, based on an existing
epidemiological model developed in 2012 by the Centers for Disease Control and Prevention.  
Economic parameters to track the cost burden of TB for the US health care system were added,
and an agent-based stochastic version of the model was implemented.  The sensitivity of the extended
model to changes in parameters was analyzed, and the percentage of foreign-born immigrants with
LTBI appears to be a highly influential parameter in the model.  Intervention strategies to reduce LTBI
among foreign-born arrivals were evaluated, and estimates of the cost per case averted were found.
